Analysis of Tick-Bourne Disease Cases Reported to DPH Between 2019-2024

### 2025-04-26 products/manuscript/Manuscript.qmd

+-----------+-----------+-----------+-----------+-----------+
| term      | estimate  | s         | statistic | p.value   |
|           |           | td.error  |           |           |
| \<chr\>   | \<dbl\>   |           | \<dbl\>   | \<dbl\>   |
|           |           | \<dbl\>   |           |           |
+:==========+==========:+==========:+==========:+==========:+
| (         | -2 3 2    | 1 57      | 1         | 0.1729390 |
| I         | 8.5151515 | 3.052665  | .48025251 |           |
| ntercept) |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| YEAR      | 1.1515152 | 0.777581  | 1         | 0.1727716 |
|           |           |           | .48089418 |           |
+-----------+-----------+-----------+-----------+-----------+
| B         | 0.4242424 | 5.484565  | 0         | 0.9400358 |
| ABESIOSIS |           |           | .07735207 |           |
+-----------+-----------+-----------+-----------+-----------+
| DENGUE    | 4.8484848 | 6.364775  | 0         | 0.4656907 |
|           |           |           | .76176850 |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | 5.0000000 | 5.157889  | 0         | 0.3576794 |
| C         |           |           | .96938889 |           |
| H         |           |           |           |           |
| AFFEENSIS |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| EHRLICHIA | -         | 6.364775  | 0         | 0.8604390 |
| EWINGII   | 1.1515152 |           | .18092002 |           |
+-----------+-----------+-----------+-----------+-----------+
| LYME      | 8.5606061 | 4.963745  | 1         | 0.1186814 |
| DISEASE   |           |           | .72462659 |           |
+-----------+-----------+-----------+-----------+-----------+
| ROCKY     | 0.5757576 | 5.484565  | 0         | 0.9186958 |
| MOUNTAIN  |           |           | .10497781 |           |
| SPOTTED   |           |           |           |           |
| FEVER     |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+
| WEST NILE | 8.2272727 | 5.593721  | 1         | 0.1754208 |
| (WNV)     |           |           | .47080497 |           |
| INFECTION |           |           |           |           |
+-----------+-----------+-----------+-----------+-----------+

@@

+--------+--------+--------+--------+--------+
| term   | e      | s t    | s t    | p      |
|        | s      | d      | a      | .value |
| \      | timate | .error | tistic |        |
| <chr\> |        |        |        | \      |
|        | \      | \      | \      | <dbl\> |
|        | <dbl\> | <dbl\> | <dbl\> |        |
+:=======+=======:+=======:+=======:+=======:+
| ( I n  | 9 9 3  | 5 7 2  | 1      | 0 .    |
| t      | 5      | 9      | .      | 1      |
| e      | .      | .      | 733920 | 434648 |
| rcept) | 267857 | 946482 |        |        |
+--------+--------+--------+--------+--------+
| YEAR   | -   4  | 2      | -   1  | 0 .    |
|        |     .  | .      |     .  | 1      |
|        | 910714 | 835202 | 732051 | 438108 |
+--------+--------+--------+--------+--------+

@@

+--------------+--------------+--------------+--------------+
|              |              |              |              |
+--------------+--------------+--------------+--------------+
|              |              |              |              |
+--------------+--------------+--------------+--------------+

@@

+--------------+--------------+--------------+--------------+
| Model Type   | Predictors   | Accuracy     | ROC AUC      |
|              | Used         |              |              |
+==============+==============+==============+==============+
| Random       | Age, Sex,    | 78.1%        | 0.68         |
| Forest       | County,      |              |              |
|              | Disease      |              |              |
+--------------+--------------+--------------+--------------+
| Random       | Poverty Rate | 88.4%        | 0.46         |
| Forest -     | By County    |              |              |
| Poverty Rate |              |              |              |
| Only         |              |              |              |
+--------------+--------------+--------------+--------------+

>>>>

+----------+----------+----------+----------+----------+
| term     | estimate | s        | s        | p.value  |
|          |          | td.error | tatistic |          |
| \<chr\>  | \<dbl\>  |          |          | \<dbl\>  |
|          |          | \<dbl\>  | \<dbl\>  |          |
+:=========+=========:+=========:+=========:+=========:+
| ( I      | -2 3 2   | 1 57     | 1        | 0        |
| n        | 8        | 3.052665 | .        | .1729390 |
| tercept) | .5151515 |          | 48025251 |          |
+----------+----------+----------+----------+----------+
| YEAR     | 1        | 0.777581 | 1        | 0        |
|          | .1515152 |          | .        | .1727716 |
|          |          |          | 48089418 |          |
+----------+----------+----------+----------+----------+
| B        | 0        | 5.484565 | 0        | 0        |
| A        | .4242424 |          | .        | .9400358 |
| BESIOSIS |          |          | 07735207 |          |
+----------+----------+----------+----------+----------+
| DENGUE   | 4        | 6.364775 | 0        | 0        |
|          | .8484848 |          | .        | .4656907 |
|          |          |          | 76176850 |          |
+----------+----------+----------+----------+----------+
| E        | 5        | 5.157889 | 0        | 0        |
| HRLICHIA | .0000000 |          | .        | .3576794 |
| C H      |          |          | 96938889 |          |
| A        |          |          |          |          |
| FFEENSIS |          |          |          |          |
+----------+----------+----------+----------+----------+
| E        | -   1    | 6.364775 | 0        | 0        |
| HRLICHIA | .1515152 |          | .        | .8604390 |
| EWINGII  |          |          | 18092002 |          |
+----------+----------+----------+----------+----------+
| LYME     | 8        | 4.963745 | 1        | 0        |
| DISEASE  | .5606061 |          | .        | .1186814 |
|          |          |          | 72462659 |          |
+----------+----------+----------+----------+----------+
| ROCKY    | 0        | 5.484565 | 0        | 0        |
| MOUNTAIN | .5757576 |          | .        | .9186958 |
| SPOTTED  |          |          | 10497781 |          |
| FEVER    |          |          |          |          |
+----------+----------+----------+----------+----------+
| WEST     | 8        | 5.593721 | 1        | 0        |
| NILE     | .2272727 |          | .        | .1754208 |
| (WNV)    |          |          | 47080497 |          |
| I        |          |          |          |          |
| NFECTION |          |          |          |          |
+----------+----------+----------+----------+----------+

@@

+-------+-------+-------+-------+-------+
| term  | e s   | s t d | s t a | p     |
|       | t     | .     | t     | .     |
| \     | imate | error | istic | value |
| \<    |       |       |       |       |
| chr\> | \     | \     | \     | \     |
|       | \<    | \<    | \<    | \<    |
|       | dbl\> | dbl\> | dbl\> | dbl\> |
+:======+======:+======:+======:+======:+
| ( I n | 9 9 3 | 5 7 2 | 1 .   | 0 . 1 |
| t e   | 5 .   | 9 .   | 7     | 4     |
| r     | 2     | 9     | 33920 | 34648 |
| cept) | 67857 | 46482 |       |       |
+-------+-------+-------+-------+-------+
| YEAR  | -   4 | 2 .   | -   1 | 0 . 1 |
|       |     . | 8     |     . | 4     |
|       |     9 | 35202 |     7 | 38108 |
|       | 10714 |       | 32051 |       |
+-------+-------+-------+-------+-------+

@@

+-------------+-------------+-------------+-------------+
|             |             |             |             |
+-------------+-------------+-------------+-------------+
|             |             |             |             |
+-------------+-------------+-------------+-------------+

@@

+-------------+-------------+-------------+-------------+
| Model Type  | Predictors  | Accuracy    | ROC AUC     |
|             | Used        |             |             |
+=============+=============+=============+=============+
| Random      | Age, Sex,   | 78.1%       | 0.68        |
| Forest      | County,     |             |             |
|             | Disease     |             |             |
+-------------+-------------+-------------+-------------+
| Random      | Poverty     | 88.4%       | 0.46        |
| Forest -    | Rate By     |             |             |
| Poverty     | County      |             |             |
| Rate Only   |             |             |             |
+-------------+-------------+-------------+-------------+
